---
title: "delta8tweets"
author: "Drew Walker"
date: "6/9/2021"
output: html_document
bibliography: references.bib
---
# Tidy Adaptation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#remotes::install_github("slu-openGIS/postmastr")
library(stm)
library(here)
library(postmastr)
library(textmineR)
library(tidyverse)
library(tidytext)
library(knitr) #Create nicely formatted output tables
library(kableExtra) #Create nicely formatted output tables
library(formattable) #For the color_tile function
library(lubridate)
library(academictwitteR)
library(tm)
library(tidygeocoder)
library(ggpubr)
library(topicmodels)

APIToken <- read_csv("apikeys.csv")
api_key <- as.character(APIToken[1,1])
api_secret_key <- as.character(APIToken[1,2])
bearer_token <- as.character(APIToken[1,3])
```

# Resources for topic modeling

Tidy Text Mining With R (Julia Silge) <https://www.tidytextmining.com/topicmodeling.html>

Predominantly used: has some older code that i had to fix, may try to convert to Julia's topicmodels package <https://towardsdatascience.com/beginners-guide-to-lda-topic-modelling-with-r-e57a5a8e7a25>

# Pull tweet full archive tweet data

-   Add search by hashtag

```{r get-hashtag-delta8-tweets}

#Get tweets with Delta 8 thc or delta 8 hashtag

hashtag_delta8_tweets_jan_2020 <-  get_all_tweets("#delta8",
                 "2020-01-01T00:00:00Z",
                 "2021-07-13T00:00:00Z",
                 bearer_token)
users_hashtag_d8_tweets_jan_2020 <-
  get_user_profile(unique(hashtag_delta8_tweets_jan_2020$author_id), bearer_token)

users_hashtag_d8_tweets_jan_2020 <- users_hashtag_d8_tweets_jan_2020 %>% 
  rename(author_id = id)


hashtag_delta8_tweets_and_user_info_jan_2020 <- left_join(hashtag_delta8_tweets_jan_2020, users_hashtag_d8_tweets_jan_2020, by = "author_id")

write_rds(hashtag_delta8_tweets_and_user_info_jan_2020, "hashtag_delta8_tweets_and_user_info_jan_2020.rds")
```

# Tweet data NLP and trend analysis

```{r delta8tweets,}
d8_tweets <- readRDS("hashtag_delta8_tweets_and_user_info_jan_2020.rds")
d8_tweets <- d8_tweets
```

# prepping for nlp

Decision was made to remove stopwords post hoc, due to inclusion of bigrams, and recent reseearch recommending for adhoc removeal instead. [@schofield2017]

-   [@boon-itt2020] removed urls, emojis, special characters, retweets, hashtag symbols, hyperlinks.

    -   Also removed stopwords, lower cased, digits, words like delta8, delta, thc, http

```{r, preprocessing-tweets}

d8_tweets_text_id <- d8_tweets %>% 
  select(text,id)

#Token unnesting 

#Remove @ and RT tweet notation
d8_tweets$text <- gsub("RT.*:", "", d8_tweets$text)
d8_tweets$text <- gsub("@.* ", "", d8_tweets$text)
# sub out digits , punctuation
#Should digits be included in case of delta 8, delta 10? 

d8_tweets$text <- gsub('[[:punct:]]+', '', d8_tweets$text)
text_cleaning_tokens <- d8_tweets %>% 
  tidytext::unnest_tokens(word, text) %>% 
  left_join(d8_tweets_text_id, by = "id") %>%
  mutate(raw_text = text)
#remove words? like 

text_cleaning_tokens$word <- gsub('[[:digit:]]+', '', text_cleaning_tokens$word)
text_cleaning_tokens$word <- gsub('https|delta|delta 8|thc', '', text_cleaning_tokens$word)
#remove anything where word is only 1 character like a i d, remove stopwords
text_cleaning_tokens <- text_cleaning_tokens %>% filter(!(nchar(word) == 1))%>% 
  anti_join(stop_words)
#Stem/lemmatizer?
# https://blogs.cornell.edu/cornellnlp/2019/02/09/choose-your-words-wisely-for-topic-models/ 
# may not need to, is often done to save resources, or combine multiple words to mean same thing. May try to do as a sensitivity check 

#remove commonly occurring words


#remove spaces
text_cleaning_tokens <- text_cleaning_tokens %>% 
  count(id,word) %>% 
  filter(word != "")
```

# Create document term matrix

```{r, create-dtm}
#create DTM
tweet_dtm <- text_cleaning_tokens %>% 
  cast_dtm(id,word,n)
```

# Running lda on up to 20 clusters, determining number of ks for analysis by highest coherence score

-   We evaluated lda models using 1-20 clusters, and chose to conduct the analysis using 3 clusters due to the highest coherence score.

-   We tried others inaugural_dfmas a sensitivity analysis

```{r test-model}
ldatest_tweet <- LDA(tweet_dtm,k=5,control = (list(seed = 5849)))
```


```{r, evaluate-model}
tweet_topics <- tidy(ldatest_tweet, matrix = "beta")
tweet_topics
```

```{r, evaluate words}
  
d8_top_terms <- tweet_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 15) %>% 
  ungroup() %>%
  arrange(topic, -beta)

d8_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```



```{r, lda}
library(furrr)
plan(multiprocess)

models <- tibble(K = 2:12) %>%
  mutate(topic_model = future_map(K, ~LDA(tweet_dtm,k = ., control = list(seed = 5849))))

current_time <- Sys.time()
st <- format(current_time,"%Y-%m-%d_%H_%M",)

rdsfilename <- paste0(here("summarysave"),st,".rds") 
saveRDS(models, rdsfilename)
```

```{r, get-top-words}
plan(multiprocess)
models_tidy <- models %>% 
  mutate(tweet_topics = future_map(tidy(topic_model,matrix = "beta")))
```




# generating label topics

A label topic procedure was used using the textmineR GetProbableTerms function, which extracted terms (uni and bigrams) which are "more probable [in a set of topics] than a corpus overall".


# Sentiment Analysis

```{r, nrc}
nrc <- get_sentiments("nrc") # get specific sentiment lexicons in a tidy format

nrc_words <- tf %>%
  rename(word = term) %>% 
  inner_join(nrc, by="word")

pie_words<- nrc_words %>%
  group_by(sentiment) %>% # group by sentiment type
  tally %>% # counts number of rows
  arrange(desc(n)) # arrange sentiments in descending order based on frequency
pieFileName <- paste0(here("piewords"),st,".png") 

nrc_pie_chart <- ggplot(pie_words, aes(x= fct_reorder(sentiment,n),y = n, fill = sentiment)) + 
          geom_bar(position = "dodge", stat = "identity")+
  xlab("NRC Sentiment")+
  ylab("Word Count in Delta 8 Tweets")+
  coord_flip()+
  theme_classic2()+
  theme(legend.position = "none")
nrc_pie_chart

ggsave(pieFileName)


```
